Approaching Optimal Duplicate Detection in a Sliding Window

### 2020-05-10 article_content.tex
update

@@

\paragraph{Compact Short Hash Filter (CSHF)}
%\subsection{Compact Short Hash Filter}
Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF). The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, one stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.

@@

\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window of size $2M + w\log_2 w$.

@@

	On the other hand, a duplicate $e^\star \dup E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN. Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}. Then $e^\star$ triggers a false negative with probability
	\begin{align*}
	\FN_n &= (1 - \Pr[C | D])(1-p) \\ &=  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
	&= \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) \\
	&=  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p)\\
	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
	\end{align*}
	Hence, the error probability of the filter is
	\begin{align*}
	EP_n 
	& = \FN_n + p \\
	&=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p\\
	EP_n & = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
	\end{align*}
	which is minimized when $p = 0$. 
	\end{proof}

@@

%As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and Bloom filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP. This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.

>>>>

A literature review collects the following DDF constructions: A2 filters \cite{Yoo10}, Stable Bloom Filters (SBF) \cite{Den06}, Quotient Hash Tables (QHT) \cite{10.1145/3297280.3297335}, Streaming Quotient Filters (SQF) \cite{Dut13}, Block-decaying Bloom Filters (b\_DBF) \cite{She08}, and a slight variation of Cuckoo Filters \cite{Fan14} suggested by \cite{10.1145/3297280.3297335}. The structure proposed in \cite{10.1145/1060745.1060753} is not designed for wDDP but a variant called `landmark` sliding window, which consists of a zero-resetting of the memory at some user-defined epochs.

@@

\paragraph{Compact Short Hash Filter (CSHF)}
%\subsection{Compact Short Hash Filter}
Removing the dictionary from the SHF construction yields a more memory-efficient, but less time-efficient construction, which we dub \enquote{compact} short hash filter (CSHF). The CSHF performs in linear time in $w$, and is a simple queue, the only point is that instead of storing $e$, the filter stores $h(e)$, where $h$ is a hash function of codomain size $\lfloor \frac Mw \rfloor$.% and is described in Algorithm~\ref{alg:CSHF}.

@@

\paragraph{Remark:} A CSHF of size $M$ on a sliding window $w$ has the same error rate than an SHF of sliding window $w$ of size $2M + w\log_2 w$.

@@

	On the other hand, a duplicate $e^\star \in E$ is classified as \UNSEEN if and only if it was not seen in the last $M$ elements of the stream, and the filter answers \UNSEEN. Let $D$ be the event \enquote{\emph{There is at least one duplicate in the stream}} and $C$ be the event \enquote{\emph{There is a duplicate of $e^\star$ in the $M$ previous elements of the stream}}. Then $e^\star$ triggers a false negative with probability
	\begin{align*}
	\FN_n &= (1 - \Pr[C | D])(1-p) \\ &=  \left(1 - \frac{\Pr[C \cap D]}{\Pr[D]}\right)(1-p)\\
	&= \left(1 - \frac{\Pr[C]}{\Pr[D]}\right)(1-p) \\
	&=  \left(1 - \frac{1 - \Pr[\bar C]}{1 - \Pr[\bar D]}\right)(1-p)\\
	\FN_n &=  \left(1 - \frac{1 - \left(1 - \frac 1{|\Gamma|}\right)^M}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p)
	\end{align*}
	Hence, the error probability of the filter is
	\begin{align*}
	EP_n 
	& = \FN_n + p \\
	&=  \left(1 - \frac{1 - \left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}\right)(1-p) + p\\
	EP_n & = 1 - \frac{1-\left(1 - \frac{1}{|\Gamma|}\right)^{M}}{1 - \left(1 - \frac 1{|\Gamma|}\right)^n}(1-p),
	\end{align*}
	which is minimized when $p = 0$. 
	\end{proof}

@@

%As noted in Section~\ref{sub:related}, A2 filters are a primitive form of a queuing filter (with $L=2$ and  filters as subfilters) and thus were not included in this benchmark, as we focused on adapting filters designed for DDP to the sliding window DDP. This raises the question of whether recursive constructions (queuing filters of queuing filters) have particularly interesting properties, which we leave open for future work.
